\section{Quantum Coherence and Population Transfer in a Driven Cascade Three-Level Artificial Atom}
  A 3-level atom is measured. It is found that the Rabi splitting between of the levels agrees with the transmon-resonator coupling strength ratio:
  \[
  	g_{j+1}/g_j \sim \sqrt{j+1}.
  \]
 
 \ipicCaption{4cm}{QuantumCoherenceTransferDrivenCascadeThreeLevelArtificialAtom}{Two tone measurement is done to find the splitting \iket{1}-\iket{2}. The heights $ \alpha, \beta $ correspond to the population of levels $ \rho_{11} $ and $ \rho_{22} $.}
 
 Rabi oscillation measurements are used to find the relaxation rates $ \Gamma_{10}, \gamma_{10}, \Gamma_{21}, \gamma_{20}$. With this in mind, we begin using fields
 
 \begin{itemize}
 	\item $ \Omega_U = \Omega_{21} $;
 	\item $ \Omega_L  = \Omega_{10}$,
 \end{itemize}

\noindent to pump the atoms. \ipic{4cm}{QuantumCoherenceTransferDrivenCascadeThreeLevelArtificialAtom1}. The stronger one acts as the pump, while the weaker acts as a probe.

\iframe{\red{The stronger drive causes the levels to splits. The weaker pump will be able to probe this splitting. \ipic{6cm}{QuantumCoherenceTransferDrivenCascadeThreeLevelArtificialAtom2}}}
 
 The splitting is monitored specifically, by increasing the power of the driving field (y-axis) and sweeping with the second probe tone. Essentially we are monitoring the sweeping of the 2nd level in each case. \textbf{\red{Driving the lower transition weakens the splitting as it increases. Driving the upper transition does NOT diminish the splitting being probed. The authors say that this is due to the decay rates $ \gamma_{10} $ and $ \gamma_{20} $}}
 
 \ipicCaption{5cm}{QuantumCoherenceTransferDrivenCascadeThreeLevelArtificialAtom5}{When splitting of \iket{1} is caused by the lower drive, the probe signal gets weaker.} %This is because this splitting drive is also responsible for populating level \iket{1}, and as the splitting increases, this population weakens and the probe tone will not work.}
 
 The splitting of the peaks, as a function of the driving field amplitude give a linear relationship, as expected for Rabi splitting $ \sim \Omega\sqrt{N} $.
 
 \ipic{5cm}{QuantumCoherenceTransferDrivenCascadeThreeLevelArtificialAtom6}
 
 \newpage
 